\Title

### 2021-01-26 manuscript/manuscript.tex
Cite Boule in the australia section
Move texts marked for discussions to discussion

\textbf{NOTE: This paragraph might be better in the Discussion section.}

@@

We computed the gravity disturbance by removing the normal gravity of
the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
Here, normal gravity was computed at each observation point through the
closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
Finally, we convert the observations to planar Cartesian coordinates by
applying a Mercator projection.

@@

FOR DISCUSSION:

>>>>

@@

We computed the gravity disturbance by removing the normal gravity of
the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
Here, normal gravity was computed at each observation point through the
closed-form formula of \citet{ligotze2001} using the Boule software
\citep{boule2020}.
Finally, we convert the observations to planar Cartesian coordinates by
applying a Mercator projection.

@@
